## Setup

```{r}
#| label: setup
library(tidyverse)
library(janitor)
library(data.table)
library(readxl)
library(vdemdata)
library(zoo)
library(democracyData)
library(fuzzyjoin)
library(survival)
```

## leaders dataset

### Archigos Dataset

```{r}
#| label: archigos

# read_data
Archigos <- fread("http://ksgleditsch.com/data/1March_Archigos_4.1.txt", encoding = "Latin-1")

write_csv(Archigos, "Archigos.csv")

archigos <- Archigos |>
  mutate(startdate = ymd(startdate),
         enddate = ymd(enddate)) |> 
  #update Léon M'ba of Babon and Pution
  filter(!obsid %in% c("GAB-1960", "GAB-1964-1")) |>
  mutate(
    startdate = case_when(
      obsid == "GAB-1964-2" ~ ymd("1960-08-17"),
      obsid == "CHA-1990" ~ ymd("1990-12-2"),
      obsid == "RUS-2000" ~ ymd("1999-12-31"),
      TRUE ~ startdate),
    entry = case_when(
      obsid == "GAB-1964-2" ~ "Regular",
      TRUE ~ entry)
  )

write_csv(archigos, "archigos.csv")
```

### PLAD Dataset

```{r}
download.file("https://dataverse.harvard.edu/api/access/datafile/10119324", "PLAD.xls")

# read_data
PLAD <- read_excel("PLAD.xls") |> 
  mutate(exit = case_when(
    exit == "Still in office" ~ "Still in Office",
    TRUE ~ exit
  ))
write_csv(PLAD, "PLAD.csv")

plad <- PLAD |> 
  select(country, continent, 1:6, entry, exit, gender, yrborn, birthdate) |>
  mutate(
    startdate = dmy(startdate),
    birthdate = dmy(birthdate),
    enddate = case_when(exit == "Still in Office" ~ Sys.Date(),
                             .default = dmy(enddate)),
    yrborn = as.numeric(yrborn)
  ) 
# |>
#   filter(enddate - startdate > 270)
write_csv(plad, "plad.csv")
```

### Leaders Dataset: Archigos and PLAD

```{r}
#| label: leaders_Reddy

leaders <- archigos |>
  filter(enddate - startdate > 270) |>
  full_join(plad, join_by(idacr, startdate), suffix = c(".archigos", ".plad")) |>
  group_by(idacr) |>
  fill(ccode, country, continent, .direction = "downup") |>
  ungroup() |>
  mutate(
    obsid = coalesce(obsid, plad_id),
    leader.archigos = coalesce(leader.archigos, leader.plad),
    enddate.archigos = coalesce(enddate.plad, enddate.archigos),
    entry.archigos = coalesce(entry.plad, entry.archigos),
    exit.archigos = coalesce(exit.plad, exit.archigos),
    enddate.archigos = if_else(exit.archigos == "Still in Office", Sys.Date(), enddate.archigos),
    gender.archigos = coalesce(gender.archigos, gender.plad),
    yrborn.archigos = coalesce(yrborn.archigos, as.numeric(yrborn.plad)),
    exitcode = case_when(
      is.na(exitcode) ~ exit.archigos,
      exitcode == "Still in Office" & exit.archigos != "Still in office" ~ exit.archigos,
    TRUE ~ exitcode),
    exitcode = case_when(
      leader.archigos %in% c("Mugabe", "Al-Bashir", "Ibrahim Boubacar Keita", "Win Myint", "Deby", "Conde", "Bah Ndaw", "Roch Marc Christian Kabore", "Paul-Henri Sandaogo Damiba", "Ali Bongo Ondimba", "Mohamed Bazoum") ~ "Coup",
      TRUE ~ exitcode
    )
  ) |> 
  select(1:4, country, continent, leader = leader.archigos, startdate, enddate = enddate.archigos, entry = entry.archigos, exit = exit.archigos, exitcode, gender = gender.archigos, yrborn = yrborn.archigos) |>
  arrange(ccode, startdate)
write.csv(leaders, "leaders.csv")
```

## Coup analysis dataset

### Political Violence Dataset: MEPV

```{r}
#| label: violence

download.file("http://www.systemicpeace.org/inscr/MEPVv2018.xls", "political_violence_2018.xls")

political_violence <- read_excel("political_violence_2018.xls") |> 
  dplyr::select(ccode, year, violence = actotal)
```

### GDP and population Dataset

```{r}
#| label: GDP_pop
GDP <- vdem |> 
  select(ccode = COWcode, country = country_name, year, GDP_pc = e_gdppc, pop = e_pop) |>
  filter(year >= 1900)|> 
  # create a new variable for 5-year moving average of GDP growth
  mutate(GDP_trend = GDP_pc / lag(rollapply(GDP_pc, width = 5, FUN = mean,
                               align = 'right', fill = NA)),
         .by = c(ccode)) |> 
  mutate(pop_log = log(pop)) |>
  select(ccode, year, GDP_pc, GDP_trend, pop_log)
```

### Regime Type Dataset

```{r}
#| label: regimes
regimes <- REIGN |>
  select(
    ccode = GWn, 
    country = extended_country_name, 
    year, 
    regime_type = gwf_regimetype) |> 
  filter(year > 1900,
         !str_detect(regime_type, "provisional"),
         !regime_type  %in% c("warlordism", "foreign-occupied")) |>
  distinct(ccode, year, .keep_all = T) |> 
  mutate(
    regime_coup = case_when(
      regime_type %in% c(
        "party-based",
        "party-personal",
        "party-military",
        "party-personal-military",
        "oligarchy"
      ) ~ "dominant-party",
      regime_type == "personal" ~ "personal",
      regime_type %in% c("military", "military personal", "indirect military") ~ "military",
      regime_type == "monarchy" ~ "monarchy",
      regime_type %in% c("presidential", "parliamentary") ~ "democracy",
      TRUE ~ "other"
    ),
    regime_autocoup = case_when(
      regime_type %in% c(
        "party-based",
        "party-personal",
        "party-military",
        "party-personal-military",
        "oligarchy"
      ) ~ "dominant-party",
      regime_type == "personal" ~ "personal",
      regime_type %in% c("military", "military personal", "indirect military") ~ "military",
      regime_type == "monarchy" ~ "monarchy",
      regime_type == "presidential" ~ "presidential",
      regime_type == "parliamentary" ~ "parliamentary",
      TRUE ~ NA
    )
  ) |>
  filter(year > 1944) |> 
  dplyr::select(country, ccode, year, regime_coup, regime_autocoup)
```

### Coup_all Dataset

```{r}
#| label: coup_all

# Coups1 <- fread("https://www.uky.edu/~clthyn2/coup_data/candidate_dataset.txt")
# Coups2 <- fread("https://www.uky.edu/~clthyn2/coup_data/powell_thyne_coups_final.txt")
# Coups3 <- fread("https://www.uky.edu/~clthyn2/coup_data/powell_thyne_ccode_year.txt")

coup_all <- fread("https://www.uky.edu/~clthyn2/coup_data/powell_thyne_ccode_year.txt") |> 
  mutate(coup = case_when(
    coup1 == 0 ~ 0,
    coup1 == 2 | coup2 == 2 | coup3 == 2 | coup4 == 2 ~ 2,
    TRUE ~ 1
  )) |>
  group_by(ccode) |> 
  arrange(year) |> 
  mutate(pre_coups = lag(cumsum(coup %in% c(1, 2)), default = 0),
         last_coup_year = lag(case_when(coup %in% c(1, 2)  ~ year,
                                        TRUE ~ NA_integer_)),
         last_coup_year = case_when(year == min(year) ~ year,
                                    TRUE ~ last_coup_year)) |> 
  fill(last_coup_year, .direction = "down") |>
  mutate(time_since_last_coup = year - last_coup_year,
         coup_dummy = case_when(pre_coups == 0 ~ 0,
                                TRUE ~ 1)) |>
  dplyr::select(ccode, year, coup, pre_coups, time_since_last_coup, coup_dummy) 
```

### Coup Analysis Dataset

```{r}
#| label: coup_analysis

coup_model <- regimes |> 
  filter(regime_coup != "other",
         year > 1949) |>
  left_join(coup_all, by = join_by(ccode, year)) |> 
  left_join(political_violence, by = join_by(ccode, year)) |>
  left_join(GDP, by = join_by(ccode, year)) |> 
  filter(!is.na(GDP_pc)) |> 
  mutate(violence = na.locf(violence, .by = ccode)) |>
  mutate(regime = fct_relevel(regime_coup, "dominant-party"),
         ect = (GDP_trend-1)*100) |> 
  select(ccode, country, year, coup, regime = regime_coup, GDP_trend = ect, GDP_pc, violence, pre_coups, coup_dummy, time_since_last_coup)

write.csv(coup_model, "coup_model.csv")
```

## Autocoup analysis Dataset

### Autocoup Dataset

```{r}
#| label: autocoup
# read_data
Autocoup <- read_excel("Autocoup.xlsx", na = "Incumbent") |> 
  mutate(exit_date = replace_na(exit_date, Sys.Date()))

autocoup <- Autocoup |> 
  select(1:14) |>
  mutate(entry_date = as.Date(entry_date),
         exit_date = as.Date(exit_date ))  |> 
  mutate(extending_date = make_date(year = extending_date, 
                                    month = month(entry_date), 
                                    day = day(entry_date)))

write_csv(autocoup, "autocoup.csv")
```

### Leader_autocoup Dataset

```{r}
leader_autocoup <- leaders |> 
  left_join(autocoup, join_by(ccode, startdate == entry_date)) |>
  mutate(autocoup_attempt = if_else(is.na(leader_name), 0, 1),
         autocoup_success = if_else(!is.na(extending_date), 1,
                                    if_else(!is.na(autocoup_attempt), 0, NA)),
         base_year = year(startdate + as.numeric(difftime(enddate, startdate, units = "days")) / 2),
         base_year = coalesce(autocoup_date, base_year),
         age = base_year - yrborn) |>
  select(1:2, leader, leader_name, age, everything())

# leader_autocoup |> 
#   select(leader, country.x, country.y) |>
#   view()
```

### Polity5 Dataset

```{r}
polity5 <- democracyData::polity5 |> 
  mutate(polity5 = ifelse(polity < -10, NA, polity)) |>
  select(ccode = polity_annual_ccode, year, polity5) |> 
  group_by(ccode) |>
  fill(polity5, .direction = "up") |>
  ungroup() |>
  filter(year >= 1945)
```

### Autocoup Analysis Dataset

```{r}
#| label: autocoup_analysis

autocoup_model <- leader_autocoup |> 
  filter(base_year > 1949) |>
  left_join(regimes, join_by(ccode, base_year == year)) |> 
  group_by(ccode) |>
  fill(regime_autocoup, .direction = "updown") |>
  ungroup() |> 
  left_join(political_violence, by = join_by(ccode, base_year == year)) |> 
  mutate(violence = na.locf(violence, .by = ccode)) |> 
  left_join(GDP, by = join_by(ccode, base_year == year)) |> 
  filter(!is.na(GDP_pc)) |> 
  left_join(polity5, by = join_by(ccode, base_year == year)) |> 
  select(ccode, country, base_year, leader, autocoup_attempt, autocoup_outcome, regime = regime_autocoup, GDP_pc, GDP_trend, polity5, violence, age, pop_log)

write_csv(autocoup_model, "autocoup_model.csv")
```

## Survival Analysis Dataset

```{r}
#| label: coup_data

coup_success <- fread("https://www.uky.edu/~clthyn2/coup_data/powell_thyne_coups_final.txt") |> 
  mutate(coup_date = make_date(year = year,
                               month = month, 
                               day = day)) |>
  select(ccode, country, coup_date, coup, year) |>
  filter(coup == 2)
# |> 
#   group_by(ccode, year) |>
#   filter(n() > 1) |> 
#   ungroup() |>
#   view()
```

```{r}
#| label: survival

overstay_leaders <- autocoup |> 
  filter(autocoup_outcome == "Yes") |> 
  select(1:14)

survival_data <- leaders |> 
  left_join(overstay_leaders, join_by(ccode, startdate == entry_date)) |>
  mutate(coup_exit = ifelse(exitcode %in% c("Removed by Military, without Foreign Support","Removed by Other Government Actors, without Foreign Support", "Coup"), 1, 0)) |>
  mutate(coup_entry=ifelse(lag(coup_exit==1),1,0),.by = ccode) |> 
  filter(!is.na(extending_date) | coup_entry == 1,
          year(enddate) > 1945) |> 
mutate(group = case_when(!is.na(extending_date) ~ "A",
                        .default = "B"),
enddate = case_when(leader == "Azali Assoumani" ~ Sys.Date(),
TRUE ~ enddate),
       survival_days = case_when(
         group == "A" ~ as.numeric(enddate - extending_date),
TRUE ~ as.numeric(enddate - startdate)),
year = if_else(group == "A", year(extending_date), year(startdate)),
age = year - yrborn) |>
filter(survival_days > 180 & survival_days < 18000) |>
mutate(status = case_when(
    exit %in% c(
      "Regular",
      "Natural Death",
      "Still in Office",
      "Retired Due to Ill Health") ~ 1,
    .default = 2),
startdate = coalesce(extending_date, startdate),
tstart = as.numeric(year(startdate) + (startdate - floor_date(startdate, "year"))/365),
         tstop = as.numeric(year(enddate) + (enddate - floor_date(enddate, "year"))/365)) |>
  select(ccode, country = country.x, year, leader, startdate, enddate, tstart, tstop, status, group, survival_days, age)

survival_cox_ph <- survival_data |> 
  left_join(GDP, join_by(ccode, year == year)) |> 
  left_join(polity5, join_by(ccode, year == year)) |>
  left_join(political_violence, join_by(ccode, year == year)) |>
  select(ccode, country, year, leader, age, startdate, enddate, group, survival_days, status, GDP_trend, GDP_pc, pop_log, polity5, violence)

write_csv(survival_cox_ph, "survival_cox_ph.csv")
```

```{r}
survival_cox_td <- survival_data |> 
mutate(first_year = startdate,
         last_year = enddate) |>
  survSplit(Surv(year(startdate), year(enddate), status) ~ .,
            data = _,
            cut = 1945:2022,
            id = "id",
            ) |>
  mutate(tstart = if_else(is.na(tstart), tstop, tstart)) |> 
  mutate(T1 = 0,
         T2 = ifelse(row_number() == 1, ceiling_date(first_year, "year") - first_year, 0),
         T2 = first(T2) + 365 * (row_number() - 1),
         T1 = lag(T2, default = 0),
         T2 = ifelse(row_number() == n(), survival_days, T2),
         age = age + row_number() - 1,
         .by = id) |>
  left_join(GDP, join_by(ccode, tstart == year)) |> 
  left_join(polity5, join_by(ccode, tstart == year)) |>
  left_join(political_violence, join_by(ccode, tstart == year)) |>
  drop_na() |> 
  select(id, ccode, country, leader, age, T1, T2, tstart, tstop, group, survival_days, status, GDP_trend, GDP_pc, pop_log, polity5, violence)
write_csv(survival_cox_td, "survival_cox_td.csv")
```

```{r}
survival_cox_ph |> 
mutate(group = factor(group, 
                        labels = c("Overstay leaders", "Coup-entry leaders"))) |>
  coxph(Surv(survival_days, status) ~ group + GDP_trend + GDP_pc + pop_log + polity5 + violence + age, data = _) 
```

```{r}
survival_cox_td |>
mutate(group = factor(group, 
                        labels = c("Overstay leaders", "Coup-entry leaders"))) |>
coxph(Surv(T1, T2, status) ~ group + GDP_trend + GDP_pc + pop_log + polity5 + violence + age + cluster(id), data = _)
```

## Upload Datasets

```{bash}
#| label: upload

git add .
git commit -m "Version $(date +%Y-%m-%d)"
git push
```
