## Setup

```{r}
#| label: setup

pacman::p_load(tidyverse, janitor, data.table, readxl, vdemdata, zoo, plm, democracyData, fuzzyjoin, survival, stargazer, brglm2, survminer, ggsurvfit, broom)
```

## leaders dataset

### Archigos Dataset

```{r}
#| label: archigos_data

# Download Archigos data
archigos_url <- "http://ksgleditsch.com/data/1March_Archigos_4.1.txt"
archigos_raw <- fread(archigos_url, encoding = "Latin-1")

# Clean and process Archigos data
archigos <- archigos_raw |>
  mutate(
    startdate = ymd(startdate),
    enddate = ymd(enddate),
    # Correct start dates for specific observations
    startdate = case_when(
      obsid == "GAB-1964-2" ~ ymd("1960-08-17"),
      obsid == "CHA-1990" ~ ymd("1990-12-2"),
      obsid == "RUS-2000" ~ ymd("1999-12-31"),
      TRUE ~ startdate
    ),
    entry = case_when(
      obsid == "GAB-1964-2" ~ "Regular",
      TRUE ~ entry
    )
  ) |>
  filter(
    !obsid %in% c("GAB-1960", "GAB-1964-1"),
    startdate != enddate
  )

# Save cleaned Archigos data
write_csv(archigos, "archigos_clean.csv")
```

### PLAD Dataset

```{r}
#| label: plad_data

# Download PLAD data
plad_url <- "https://dataverse.harvard.edu/api/access/datafile/10119324"
download.file(plad_url, "PLAD.xls")

# Read and process PLAD data
plad_raw <- read_excel("PLAD.xls") |>
  mutate(
    exit = case_when(
      exit == "Still in office" ~ "Still in Office",
      TRUE ~ exit
    )
  )

# Save cleaned PLAD data
write_csv(plad_raw, "plad_clean.csv")

plad <- plad_raw |>
  select(country, continent, 1:6, entry, exit, gender, yrborn, birthdate) |>
  mutate(
    startdate = dmy(startdate),
    birthdate = dmy(birthdate),
    enddate = case_when(
      exit == "Still in Office" ~ Sys.Date(),
      TRUE ~ dmy(enddate)
    ),
    yrborn = as.numeric(yrborn)
  ) |>
  filter(startdate != enddate)

# Save processed PLAD data for further analysis
write_csv(plad, "plad_processed.csv")
```

### Leaders Dataset: Archigos and PLAD

```{r}
#| label: leaders_combined

# Combine Archigos and PLAD data
leaders <- archigos |>
  full_join(plad, by = join_by(idacr, startdate), suffix = c(".archigos", ".plad")) |>
  group_by(idacr) |>
  fill(ccode, country, continent, .direction = "downup") |>
  ungroup() |>
  mutate(
    obsid = coalesce(obsid, plad_id),
    leader = coalesce(leader.archigos, leader.plad),
    enddate = coalesce(enddate.plad, enddate.archigos),
    entry = coalesce(entry.plad, entry.archigos),
    exit = coalesce(exit.plad, exit.archigos),
    enddate = if_else(exit == "Still in Office", Sys.Date(), enddate),
    gender = coalesce(gender.archigos, gender.plad),
    yrborn = coalesce(yrborn.archigos, as.numeric(yrborn.plad)),
    age = year(enddate) - yrborn,
    exitcode = case_when(
      is.na(exitcode) ~ exit,
      exitcode == "Still in Office" & exit != "Still in office" ~ exit,
      TRUE ~ exitcode
    ),
    exitcode = case_when(
      leader %in% c("Mugabe", "Al-Bashir", "Ibrahim Boubacar Keita", "Win Myint", "Deby", "Conde", "Bah Ndaw", "Roch Marc Christian Kabore", "Paul-Henri Sandaogo Damiba", "Ali Bongo Ondimba", "Mohamed Bazoum") ~ "Coup",
      TRUE ~ exitcode
    )
  ) |>
  select(1:4, country, continent, leader, startdate, enddate, entry, exit, exitcode, gender, yrborn) |>
  arrange(ccode, startdate) |>
  filter(year(enddate) > 1940)

# Save combined leaders dataset
write_csv(leaders, "leaders_combined.csv")
```

```{r}
# Step 1: Filter out leaders with less than 180 days in office
df <- leaders |>
  select(-(1:2), -continent) |>
  mutate(total_days_in_office = as.numeric(difftime(enddate, startdate, units = "days")))
# |>
#   filter(total_days_in_office >= 180) # Remove leaders with less than 180 days in office

# Step 2: Create country-year observations
df_expanded <- df |>
  # 1. 计算起始和结束年份，并为每一行生成年份序列的列表
  mutate(year = map2(year(startdate), year(enddate), seq)) |>
  # 2. 使用 unnest 展开年份列表列，其他所有列会自动保留和复制
  unnest(year) |>
  # Step 3: Remove leaders who assumed power after June 30 (keep leaders with over 180 days in office)
  mutate(
    # For each year, calculate the number of days the leader was in office
    year_start_date = as.Date(paste(year, "-01-01", sep = "")), # Start of the year
    year_end_date = as.Date(paste(year, "-12-31", sep = "")), # End of the year
    days_in_office = pmax(0, as.numeric(difftime(pmin(enddate, year_end_date),
      pmax(startdate, year_start_date),
      units = "days"
    )))
  ) |>
  # Only keep leaders with more than 180 days in office
  # filter(days_in_office >= 180) |>
  # Step 4: Create a cumulative sum of days in office for each leader across years
  group_by(country, leader) |>
  mutate(cumulative_days_in_office = cumsum(days_in_office)) |>
  ungroup() |>
  select(-year_start_date, -year_end_date) # Remove unnecessary columns

leader_year <- df_expanded |>
  mutate(age = year - yrborn) |>
  select(1:3, year, everything())


# Save the cleaned dataset
write.csv(leader_year, "leader_year.csv", row.names = FALSE)
```

## Autocoup analysis dataset

### Polity5 Dataset

```{r}
#| label: polity5_data

polity5 <- democracyData::polity5

polity <- polity5 |>
  mutate(polity5 = ifelse(polity < -10, NA, polity)) |>
  select(ccode = polity_annual_ccode, country = polity_annual_country, year, polity5) |>
  group_by(ccode) |>
  fill(polity5, .direction = "downup") |>
  mutate(
    diff1 = dplyr::lead(polity5, 1) - polity5,
    diff2 = dplyr::lead(polity5, 2) - polity5,
    diff3 = dplyr::lead(polity5, 3) - polity5,
    diff4 = dplyr::lead(polity5, 4) - polity5,
    diff5 = dplyr::lead(polity5, 5) - polity5
  ) |>
  ungroup() |>
  filter(year >= 1940)
```

### Political Violence Dataset: MEPV

```{r}
#| label: violence_data

# Download MEPV data
violence_url <- "http://www.systemicpeace.org/inscr/MEPVv2018.xls"
download.file(violence_url, "political_violence_2018.xls")

political_violence <- read_excel("political_violence_2018.xls") |>
  select(ccode, year, violence = actotal)
```

### GDP and population Dataset

```{r}
#| label: gdp_pop_data

GDP <- vdem |>
  select(ccode = COWcode, country = country_name, year, GDP_pc = e_gdppc, pop = e_pop) |>
  filter(year >= 1940) |>
  # Create a new variable for 5-year moving average of GDP growth
  mutate(
    GDP_trend = GDP_pc / lag(rollapply(GDP_pc,
      width = 5,
      FUN = mean,
      align = "right",
      fill = NA
    )),
    .by = c(ccode)
  ) |>
  mutate(pop_log = log(pop)) |>
  select(ccode, year, GDP_pc, GDP_trend, pop_log)

# vdemdata::codebook |>
#   view()
```

### Regime Type Dataset

```{r}
#| label: regimes_data

regimes <- REIGN |>
  select(
    ccode = GWn,
    country = extended_country_name,
    year,
    regime_type = gwf_regimetype
  ) |>
  distinct(ccode, year, .keep_all = T) |>
  mutate(
    regime = case_when(
      regime_type %in% c(
        "party-based",
        "party-personal",
        "party-military",
        "party-personal-military"
      ) ~ "dominant-party",
      regime_type == "personal" ~ "personal",
      regime_type %in% c("military", "military personal", "indirect military") ~ "military",
      regime_type == "presidential" ~ "presidential",
      regime_type == "parliamentary" ~ "parliamentary",
      TRUE ~ "other"
    ),
    regime_autocoup = case_when(
      regime_type %in% c(
        "party-based",
        "party-military"
      ) ~ "dominant-party",
      regime_type == "personal" ~ "personal",
      regime_type %in% c(
        "party-personal",
        "party-personal-military",
        "military personal"
      ) ~ "semi-personal",
      regime_type %in% c("military", "provisional military", "indirect military") ~ "military",
      regime_type == "presidential" ~ "presidential",
      regime_type == "parliamentary" ~ "parliamentary",
      TRUE ~ "other"
    ),
    regime_three = case_when(
      grepl("personal", regime_type) ~ "personal",
      regime_type == "presidential" ~ "presidential",
      TRUE ~ "other"
    )
  ) |>
  select(country, ccode, year, regime, regime_autocoup, regime_three, regime_type)
```

### Coup Analysis Dataset

```{r}
#| label: coup_data

# Download coup data
coup_url <- "https://www.uky.edu/~clthyn2/coup_data/powell_thyne_ccode_year.txt"
coup_raw <- fread(coup_url)
coup_total <- coup_raw |>
  mutate(
    coup = case_when(
      coup1 == 0 ~ 0,
      coup4 == 2 | (coup4 == 0 & coup3 == 2) | (coup4 == 0 & coup3 == 0 & coup2 == 2) | (coup4 == 0 & coup3 == 0 & coup2 == 0 & coup1 == 2) ~ 2,
      TRUE ~ 1
    )
  ) |>
  select(1:4, coup)
```

```{r}
coup_all <- fread(coup_url) |>
  mutate(
    coup = case_when(
      coup1 == 0 ~ 0,
      coup1 == 2 | coup2 == 2 | coup3 == 2 | coup4 == 2 ~ 2,
      TRUE ~ 1
    )
  ) |>
  group_by(ccode) |>
  arrange(year) |>
  mutate(
    pre_coups = lag(cumsum(coup %in% c(1, 2)), default = 0),
    last_coup_year = lag(case_when(
      coup %in% c(1, 2) ~ year,
      TRUE ~ NA_integer_
    )),
    last_coup_year = case_when(
      year == min(year) ~ year,
      TRUE ~ last_coup_year
    )
  ) |>
  fill(last_coup_year, .direction = "down") |>
  mutate(
    time_since_last_coup = year - last_coup_year,
    coup_dummy = case_when(
      pre_coups == 0 ~ 0,
      TRUE ~ 1
    )
  ) |>
  select(ccode, year, coup, pre_coups, time_since_last_coup, coup_dummy)

write.csv(coup_all, "coup_all.csv")
```

### Coup Analysis Model

```{r}
#| label: coup_analysis_model

coup_model <- regimes |>
  # filter(regime_coup != "other") |>
  left_join(coup_all, by = join_by(ccode, year)) |>
  left_join(political_violence, by = join_by(ccode, year)) |>
  left_join(GDP, by = join_by(ccode, year)) |>
  mutate(violence = na.locf(violence, .by = ccode, na.rm = FALSE)) |>
  mutate(
    regime = fct_relevel(regime, "dominant-party"),
    ect = (GDP_trend - 1) * 100
  ) |>
  filter(year > 1949) |>
  select(ccode, country, year, coup, regime, GDP_trend = ect, GDP_pc, violence, pre_coups, coup_dummy, time_since_last_coup)

# Save the coup analysis model
write_csv(coup_model, "coup_model.csv")
```

## Autocoup analysis Dataset

### Autocoup Dataset

```{r}
#| label: autocoup_data

# Read autocoup data
autocoup_raw <- read_excel("Autocoup.xlsx", na = "Incumbent") |>
  mutate(
    exit_date = replace_na(exit_date, Sys.Date()),
    across(everything(), str_to_sentence)
  )

autocoup <- autocoup_raw |>
  select(1:14) |>
  mutate(
    ccode = as.integer(ccode),
    entry_date = as.Date(entry_date),
    exit_date = as.Date(exit_date),
    extending_date = make_date(year = extending_date, month = month(entry_date), day = day(entry_date)),
    autocoup_date = as.integer(autocoup_date)
  )

# Save cleaned autocoup data
write_csv(autocoup, "autocoup_clean.csv")
```

### Leader_autocoup Dataset

```{r}
#| label: leader_autocoup_data

# Join leader_year and autocoup data
leader_autocoup <- leader_year |>
  left_join(
    autocoup |>
      select(ccode, leader_name, autocoup_date, autocoup_outcome, extending_date) |>
      mutate(year = autocoup_date),
    by = join_by(ccode, year)
  ) |>
  filter(days_in_office > 180) |>
  mutate(
    autocoup_attempt = if_else(is.na(leader_name), 0, 1),
    autocoup_success = if_else(!is.na(extending_date), 1, if_else(!is.na(autocoup_attempt), 0, NA))
  ) |>
  select(1:5, leader_name, everything())

# leader_autocoup |>
#   tabyl(autocoup_attempt)
```

### Autocoup Analysis Model

```{r}
#| label: autocoup_analysis_model

autocoup_model <- leader_autocoup |>
  left_join(
    regimes |>
      select(-country),
    by = join_by(ccode, year)
  ) |>
  left_join(political_violence,
    by = join_by(ccode, year)
  ) |>
  mutate(
    autocoup_outcome = case_when(
      autocoup_outcome == "Yes" ~ 2,
      autocoup_outcome == "No" ~ 1,
      TRUE ~ 0
    )
  ) |>
  left_join(GDP, by = join_by(ccode, year)) |>
  left_join(
    polity |>
      select(-country),
    by = join_by(ccode, year)
  ) |>
  group_by(ccode) |>
  fill(regime, .direction = "downup") |>
  ungroup() |>
  filter(
    year > 1944
  ) |>
  mutate(cold_war = ifelse(year > 1990, 0, 1))

write_csv(autocoup_model, "autocoup_model.csv")

# autocoup_model |>
#   tabyl(regime, autocoup_attempt) |>
#   view()
```

```{r}
# autocoup_model

attempt1 <- autocoup_model |>
  mutate(regime = factor(regime,
    levels = c("dominant-party", "personal", "presidential", "military", "parliamentary", "other")
  )) |>
  glm(
    autocoup_attempt ~ regime + GDP_pc + GDP_trend + pop_log + violence + polity5 + log(cumulative_days_in_office) + factor(cold_war),
    family = binomial,
    data = _
  )
attempt1 |>
  summary()

attempt2 <- autocoup_model |>
  mutate(regime = factor(regime,
    levels = c("dominant-party", "personal", "presidential", "military", "parliamentary", "other")
  )) |>
  glm(
    autocoup_attempt ~ regime + GDP_pc + GDP_trend + pop_log + violence + polity5 + log(cumulative_days_in_office) + factor(cold_war),
    family = binomial(link = "logit"),
    method = "brglmFit",
    data = _
  )
summary(attempt2)


stargazer(attempt1, attempt2,
  warning = FALSE,
  header = FALSE,
  type = "text"
)
```

## Survival Analysis Dataset

```{r}
#| label: leader_autocoup

# Join leader_year and autocoup data
leader_autocoup <- leader_year |>
  left_join(
    autocoup |>
      select(ccode, leader_name, autocoup_date, autocoup_outcome, extending_date) |>
      mutate(year = autocoup_date),
    by = join_by(ccode, year)
  ) |>
  # filter(days_in_office > 180) |>
  mutate(
    autocoup_attempt = if_else(is.na(leader_name), 0, 1),
    autocoup_success = if_else(!is.na(extending_date), 1, if_else(!is.na(autocoup_attempt), 0, NA))
  ) |>
  select(1:5, leader_name, everything())
```

```{r}
#| label: leader_coup_autocoup

coup_success <- fread("https://www.uky.edu/~clthyn2/coup_data/powell_thyne_coups_final.txt") |>
  mutate(coup_date = make_date(year = year, month = month, day = day)) |>
  select(ccode, country, coup_date, coup, year) |>
  filter(coup == 2)


leader_coup_autocoup <- leader_autocoup |>
  left_join(
    coup_success |>
      select(ccode, year, coup_date),
    by = join_by(ccode, year)
  ) |>
  select(1:6, coup_date, everything()) |>
  filter(!is.na(coup_date) | autocoup_success == 1) |>
  group_by(ccode, coup_date) |>
  slice_min(order_by = abs(as.numeric(coup_date - startdate)), n = 1, with_ties = T) |>
  ungroup() |>
  mutate(
    coup_to_office = abs(as.numeric(coup_date - startdate)),
    coup_to_office = ifelse(is.na(coup_to_office), 0, coup_to_office),
  ) |>
  filter(
    total_days_in_office > 180,
    coup_to_office < 170,
    !(leader == "Caldera Rodriguez" & leader_name == "Chavez")
  ) |>
  mutate(
    group = case_when(
      autocoup_success == 1 ~ "A",
      TRUE ~ "B"
    ),
    status = case_when(
      exit %in% c("Foreign", "Irregular") ~ 1,
      TRUE ~ 0
    ),
    startdate = coalesce(extending_date, startdate),
    survival_days = as.numeric(enddate - startdate),
    year = year(startdate),
    tstart = as.numeric(year(startdate) + (startdate - floor_date(startdate, "year")) / 365),
    tstop = as.numeric(year(enddate) + (enddate - floor_date(enddate, "year")) / 365)
  ) |>
  select(ccode, country, year, leader, startdate, enddate, tstart, tstop, status, group, survival_days, age)

# leaders_coup |>
#   tabyl(group)
```

```{r}
#| label: coup_autocoup_data

coup_autocoup_data <- leader_coup_autocoup |>
  left_join(
    regimes |>
      select(-country),
    by = join_by(ccode, year)
  ) |>
  left_join(political_violence,
    by = join_by(ccode, year)
  ) |>
  # mutate(
  #   autocoup_outcome = case_when(
  #     autocoup_outcome == "Yes" ~ 2,
  #     autocoup_outcome == "No" ~ 1,
  #     TRUE ~ 0
  #   )
  # ) |>
  left_join(GDP, by = join_by(ccode, year)) |>
  left_join(
    polity |>
      select(-country),
    by = join_by(ccode, year)
  ) |>
  group_by(ccode) |>
  fill(regime, .direction = "downup") |>
  ungroup() |>
  filter(
    year > 1944
  ) |>
  mutate(cold_war = ifelse(year > 1990, 0, 1))
```

```{r}
#| label: coup_autocoup_data_clean

survival_data <- coup_autocoup_data |>
  filter(
    # !(ccode == "500" & leader == "Okello"),
    # !(enddate == "2019-02-03" & leader == "Azali Assoumani"),
    # !(startdate == "1967-08-17" & leader == "Bongo"),
    !(ccode == "698" & leader == "Qabus Bin Said"),
    survival_days > 180
  ) |>
  mutate(enddate = ifelse(leader == "Azali Assoumani", Sys.Date(), enddate)) |>
  group_by(ccode) |>
  # 向下填充 categorical 或 ordinal 变量
  tidyr::fill(regime, polity5, violence, .direction = "updown") |>
  # 处理 GDP 相关变量
  mutate(
    GDP_pc = ifelse(
      is.na(GDP_pc),
      zoo::rollapply(GDP_pc, width = 3, FUN = mean, align = "right", fill = NA, na.rm = TRUE),
      GDP_pc
    ),
    GDP_trend = ifelse(
      is.na(GDP_trend),
      zoo::rollapply(GDP_trend, width = 3, FUN = mean, align = "right", fill = NA, na.rm = TRUE),
      GDP_trend
    ),
    pop_log = ifelse(
      is.na(pop_log),
      zoo::rollapply(pop_log, width = 3, FUN = mean, align = "right", fill = NA, na.rm = TRUE),
      pop_log
    )
  ) |>
  ungroup()
```

```{r}
#| label: survival_cox_ph_model

survival_cox_ph <- survival_data |>
  mutate(
    survival_year = survival_days / 365,
    regime = factor(regime,
      levels = c("dominant-party", "military", "personal", "presidential", "parliamentary", "other")
    )
  )

# Save the survival Cox PH model
write_csv(survival_cox_ph, "survival_cox_ph_model.csv")
```

```{r}
#| label: survival_cox_td_model

survival_cox_td1 <- survival_data |>
  select(ccode, country, year, leader, startdate, enddate, tstart, tstop, status, group, survival_days, age) |>
  mutate(first_year = startdate, last_year = enddate) |>
  survSplit(Surv(year(startdate), year(enddate), status) ~ ., data = _, cut = 1946:2026, id = "id") |>
  mutate(tstart = if_else(is.na(tstart), tstop, tstart)) |>
  mutate(
    T1 = 0,
    T2 = ifelse(row_number() == 1, ceiling_date(first_year, "year") - first_year, 0),
    T2 = first(T2) + 365 * (row_number() - 1),
    T1 = dplyr::lag(T2, default = 0),
    T2 = ifelse(row_number() == n(), survival_days, T2),
    age = age + row_number() - 1,
    .by = id
  )


survival_cox_td <- survival_cox_td1 |>
  left_join(
    regimes |> select(ccode, year, regime),
    by = join_by(ccode, tstart == year)
  ) |>
  left_join(
    political_violence,
    by = join_by(ccode, tstart == year)
  ) |>
  left_join(
    GDP |> select(ccode, year, GDP_pc, GDP_trend, pop_log),
    by = join_by(ccode, tstart == year)
  ) |>
  left_join(
    polity |> select(ccode, year, polity5),
    by = join_by(ccode, tstart == year)
  ) |>
  arrange(ccode, tstart) |>
  group_by(ccode) |>
  # 向下填充 categorical 或 ordinal 变量
  tidyr::fill(regime, polity5, violence, .direction = "updown") |>
  # 处理 GDP 相关变量
  mutate(
    GDP_pc = ifelse(
      is.na(GDP_pc),
      zoo::rollapply(GDP_pc, width = 3, FUN = mean, align = "right", fill = NA, na.rm = TRUE),
      GDP_pc
    ),
    GDP_trend = ifelse(
      is.na(GDP_trend),
      zoo::rollapply(GDP_trend, width = 3, FUN = mean, align = "right", fill = NA, na.rm = TRUE),
      GDP_trend
    ),
    pop_log = ifelse(
      is.na(pop_log),
      zoo::rollapply(pop_log, width = 3, FUN = mean, align = "right", fill = NA, na.rm = TRUE),
      pop_log
    )
  ) |>
  ungroup() |>
  select(id, everything()) |>
  mutate(regime = factor(regime,
    levels = c("dominant-party", "military", "personal", "presidential", "parliamentary", "other")
  ))

# Save the survival Cox TD model
write_csv(survival_cox_td, "survival_cox_td_model.csv")
```

### Running Survival Models

https://stats.oarc.ucla.edu/r/seminars/introduction-to-survival-analysis-in-r/
https://stats.oarc.ucla.edu/wp-content/uploads/2025/02/survival_r_full.html
https://stats.oarc.ucla.edu/wp-content/uploads/2025/02/intro_survival_r_code.r
https://stats.oarc.ucla.edu/wp-content/uploads/2025/02/survival_r_slides.html#/references

```{r}
#| label: run_survival_models

model_cox1 <- survival_cox_ph |>
  mutate(group = factor(group, labels = c("Autocoup leaders", "Coup-installed leaders"))) |>
  coxph(Surv(survival_days, status) ~ group + regime + GDP_trend + GDP_pc + polity5 + age + pop_log + violence, data = _)

model_cox1 |>
  summary()

model_cox2 <- survival_cox_td |>
  mutate(group = factor(group, labels = c("Autocoup leaders", "Coup-installed leaders"))) |>
  coxph(Surv(T1, T2, status) ~ group + regime + GDP_trend + GDP_pc + polity5 + age + pop_log + violence + cluster(id), data = _)

model_cox2 |>
  summary()

fit <- survfit(Surv(survival_year, status) ~ group,
  data = survival_cox_ph |>
    select(status, group, survival_year)
)
# Create log-rank plot (Kaplan-Meier plot)
ggsurvplot(fit,
  data = survival_cox_ph,
  risk.table = TRUE,
  risk.table.height = 0.3,
  pval = TRUE,
  surv.median.line = "hv",
  break.x.by = 5,
  legend.title = "Leader Type",
  legend.labs = c("Autocoup leaders", "Coup-installed leaders"),
  xlab = "Survival Years",
  # title = "Survival Curves of overstay and coup-installed leaders",
  font.title = 12
)
```

### Survival curves for Cox Model

```{r}
#| label: fig-coxSurv
#| fig-cap: Survival curves for Cox Model
#| fig-subcap:
#|  - Cox PH Model
#|  - Time-dependent Cox Model
#| layout-ncol: 2
#| echo: false

Mydata1 <- survival_cox_ph |>
  mutate(
    regime = factor(regime,
      levels = c("dominant-party", "military", "personal", "presidential", "parliamentary", "other")
    ),
    group = factor(group,
      labels = c("Autocoup leaders", "Coup-installed leaders")
    )
  ) |>
  drop_na()

testdata1 <- Mydata1 |>
  summarise(
    .by = group,
    GDP_trend = mean(GDP_trend),
    GDP_pc = mean(GDP_pc),
    pop_log = mean(pop_log),
    polity5 = mean(polity5),
    violence = mean(violence),
    age = mean(age),
    regime = factor("dominant-party",
      levels = c(
        "dominant-party", "military", "personal",
        "presidential", "parliamentary", "other"
      )
    )
  )

model_cox1 |>
  survfit(newdata = testdata1) |>
  ggsurvplot(
    data = testdata1,
    xlab = "Days",
    surv.median.line = "hv",
    legend.title = "Leader Type",
    legend.labs = c("Autocoup leaders", "Coup-installed leaders")
  )

Mydata2 <- survival_cox_td |>
  mutate(
    regime = factor(regime,
      levels = c("dominant-party", "military", "personal", "presidential", "parliamentary", "other")
    ),
    group = factor(group,
      labels = c("Autocoup leaders", "Coup-installed leaders")
    ),
    survt = (tstop - tstart) * 365
  ) |>
  drop_na()

testdata2 <- Mydata2 |>
  summarise(
    .by = group,
    GDP_trend = mean(GDP_trend),
    GDP_pc = mean(GDP_pc),
    pop_log = mean(pop_log),
    polity5 = mean(polity5),
    violence = mean(violence),
    age = mean(age),
    regime = factor("dominant-party",
      levels = c(
        "dominant-party", "military", "personal",
        "presidential", "parliamentary", "other"
      )
    )
  )

model_cox2 |>
  survfit(newdata = testdata2) |>
  ggsurvplot(
    data = testdata2,
    xlab = "Days",
    surv.median.line = "hv",
    legend.title = "Leader Type",
    legend.labs = c("Autocoup leaders", "Coup-installed leaders")
  )
```

### Hazard ratios and 95% CIs for Leader Ousting

```{r}
#| label: fig-coxHR
#| fig-cap: Hazard ratios and 95% CIs for Leader Ousting
#| fig-subcap:
#|  - Cox PH Model
#|  - Time-dependent Cox Model
#| layout-ncol: 2
#| echo: false

coxplottidy <- tidy(model_cox1, exponentiate = T, conf.int = T) |>
  mutate(term = c(
    "Coup-installed leaders",
    "Military",
    "Personal",
    "Presidential",
    "Parliamentary",
    "Ohter",
    "GDP Growth Trend",
    "GDP per capita",
    "Population: log",
    "Age",
    "Polity 5",
    "Political stability"
  ))

coxplottidy |>
  ggplot(aes(
    y = term,
    x = estimate,
    xmin = conf.low,
    xmax = conf.high
  )) +
  geom_pointrange() +
  geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "skyblue"
  ) +
  labs(x = "Hazard ratios", y = NULL, title = "") +
  theme_bw()

coxplottidy <- tidy(model_cox2, exponentiate = T, conf.int = T) |>
  mutate(term = c(
    "Coup-installed leaders",
    "Military",
    "Personal",
    "Presidential",
    "Parliamentary",
    "Ohter",
    "GDP Growth Trend",
    "GDP per capita",
    "Population: log",
    "Age",
    "Polity 5",
    "Political stability"
  ))

coxplottidy |>
  ggplot(aes(
    y = term,
    x = estimate,
    xmin = conf.low,
    xmax = conf.high
  )) +
  geom_pointrange() +
  geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "skyblue"
  ) +
  labs(x = "Hazard ratios", y = "", title = "") +
  theme_bw()
```

## Running Free_index Models

### Free_index data

```{r}
decay_factor <- 0.5
coup_autocoup <- coup_total |>
  mutate(
    coup_attemp = ifelse(coup == 0, 0, 1),
    coup_succeed = ifelse(coup == 2, 1, 0)
  ) |>
  left_join(autocoup |>
    select(ccode, year = autocoup_date, autocoup = autocoup_outcome)) |>
  mutate(
    autocoup = case_when(
      autocoup == "Yes" ~ 2,
      autocoup == "No" ~ 1,
      TRUE ~ 0
    ),
    autocoup_attemp = ifelse(autocoup == 0, 0, 1),
    autocoup_succeed = ifelse(autocoup == 2, 1, 0)
  ) |>
  left_join(
    polity |> select(-country),
    # by = join_by(ccode, year)
  ) |>
  left_join(GDP) |>
  left_join(political_violence) |>
  left_join(regimes |> select(2:3, regime)) |>
  group_by(ccode) |>
  mutate(
    # polity_diff = dplyr::lead(polity5, 3) - polity5,
    cold_war = ifelse(year > 1990, 0, 1),
    coup_attemp_3 = dplyr::lead(coup_attemp, 3),
    autocoup_attemp_3 = dplyr::lead(autocoup_attemp, 3),
    non_democracy = ifelse(regime %in% c("presidential", "parliamentary"), 0, 1),
    coup_effect = coup_attemp + lag(coup_attemp, 1) * decay_factor + lag(coup_attemp, 2) * decay_factor^2 +
      lag(coup_attemp, 3) * decay_factor^3 + lag(coup_attemp, 4) * decay_factor^4,
    coup_seffect = coup_succeed + lag(coup_succeed, 1) * decay_factor + lag(coup_succeed, 2) * decay_factor^2 +
      lag(coup_succeed, 3) * decay_factor^3 + lag(coup_succeed, 4) * decay_factor^4,
    autocoup_effect = autocoup_attemp + lag(autocoup_attemp, 1) * decay_factor + lag(autocoup_attemp, 2) * decay_factor^2 +
      lag(autocoup_attemp, 3) * decay_factor^3 + lag(autocoup_attemp, 4) * decay_factor^4,
    autocoup_seffect = autocoup_succeed + lag(autocoup_succeed, 1) * decay_factor + lag(autocoup_succeed, 2) * decay_factor^2 +
      lag(autocoup_succeed, 3) * decay_factor^3 + lag(autocoup_succeed, 4) * decay_factor^4
  ) |>
  ungroup() |>
  distinct(ccode, year, .keep_all = TRUE)

# Save democraitzation model
write_csv(coup_autocoup, "coup_autocoup.csv")
```

### Fixed effect model

```{r}
#| label: tbl-demomodel
#| tbl-cap: "The Impact of Autocoups on Democratization(1950–2018): OLS with country-fixed effects"
#| results: asis

demo_model1 <- coup_autocoup |>
  rename(Attemp = diff2, Autocoup = autocoup_attemp_3, Coup = coup_attemp_3) |>
  plm(
    Attemp ~ Autocoup + Coup + GDP_pc + GDP_trend + pop_log + violence + factor(non_democracy) + factor(cold_war),
    index = c("ccode", "year"),
    model = "within", # fixed effect
    effect = "individual",
    data = _
  )

demo_model2 <- coup_autocoup |>
  rename(Attemp = diff3, Autocoup = autocoup_attemp_3, Coup = coup_attemp_3) |>
  plm(
    Attemp ~ Autocoup + Coup + GDP_pc + GDP_trend + pop_log + violence + factor(non_democracy) + factor(cold_war),
    index = c("ccode", "year"),
    model = "within", # fixed effect
    effect = "individual",
    data = _
  )

demo_model3 <- coup_autocoup |>
  rename(Succeed = diff3, Autocoup = autocoup_effect, Coup = coup_effect) |>
  plm(
    Succeed ~ Autocoup + Coup + GDP_pc + GDP_trend + pop_log + violence + factor(non_democracy) + factor(cold_war),
    index = c("ccode", "year"),
    model = "within", # fixed effect
    effect = "individual",
    data = _
  )

demo_model4 <- coup_autocoup |>
  rename(Succeed = diff3, Autocoup = autocoup_seffect, Coup = coup_seffect) |>
  plm(
    Succeed ~ Autocoup + Coup + GDP_pc + GDP_trend + pop_log + violence + factor(non_democracy) + factor(cold_war),
    index = c("ccode", "year"),
    model = "within", # fixed effect
    effect = "individual",
    data = _
  )

stargazer(demo_model1, demo_model2, demo_model3, demo_model4,
  type = "text",
  float = F,
  header = F,
  dep.var.caption = "Dependent variable: Differences of Polity scores",
  dep.var.labels = c("Pre-event effects", "Post-event effects"),
  covariate.labels = c(
    "Autocoup", "Coup", "GDP per Capita",
    "Economic Trend", "Log Population", "Political Violence",
    "Non-Democracy", "Cold War"
  ),
  summary.logical = F,
  column.sep.width = "30pt",
  # font.size = "footnotesize",
  df = F
)
```

### Robustness tests

#### One to five years

```{r}
#| label: tbl-demomodel1
#| tbl-cap: "The Impact of Autocoups on Democratization: one to five years"
#| results: asis

demo_model1 <- plm(
  Succeed ~ Autocoup + Coup + GDP_pc + GDP_trend + pop_log + violence + factor(non_democracy) + factor(cold_war),
  index = c("ccode", "year"),
  model = "within", # fixed effect
  effect = "individual",
  data = coup_autocoup |> rename(Succeed = diff1, Autocoup = autocoup_seffect, Coup = coup_seffect)
)

demo_model2 <- plm(
  Succeed ~ Autocoup + Coup + GDP_pc + GDP_trend + pop_log + violence + factor(non_democracy) + factor(cold_war),
  index = c("ccode", "year"),
  model = "within", # fixed effect
  effect = "individual",
  data = coup_autocoup |> rename(Succeed = diff2, Autocoup = autocoup_seffect, Coup = coup_seffect)
)

demo_model3 <- plm(
  Succeed ~ Autocoup + Coup + GDP_pc + GDP_trend + pop_log + violence + factor(non_democracy) + factor(cold_war),
  index = c("ccode", "year"),
  model = "within", # fixed effect
  effect = "individual",
  data = coup_autocoup |> rename(Succeed = diff3, Autocoup = autocoup_seffect, Coup = coup_seffect)
)

demo_model4 <- plm(
  Succeed ~ Autocoup + Coup + GDP_pc + GDP_trend + pop_log + violence + factor(non_democracy) + factor(cold_war),
  index = c("ccode", "year"),
  model = "within", # fixed effect
  effect = "individual",
  data = coup_autocoup |> rename(Succeed = diff4, Autocoup = autocoup_seffect, Coup = coup_seffect)
)

demo_model5 <- plm(
  Succeed ~ Autocoup + Coup + GDP_pc + GDP_trend + pop_log + violence + factor(non_democracy) + factor(cold_war),
  index = c("ccode", "year"),
  model = "within", # fixed effect
  effect = "individual",
  data = coup_autocoup |> rename(Succeed = diff5, Autocoup = autocoup_seffect, Coup = coup_seffect)
)

stargazer(demo_model1, demo_model2, demo_model3, demo_model4, demo_model5,
  type = "text",
  float = F,
  header = F,
  dep.var.caption = "Dependent variable: Differences of Polity scores",
  dep.var.labels = "Years after the event",
  covariate.labels = c(
    "Autocoup", "Coup", "GDP per Capita",
    "Economic Trend", "Log Population", "Political Violence",
    "Non-Democracy", "Cold War"
  ),
  summary.logical = F,
  column.sep.width = "10pt",
  # font.size = "footnotesize",
  df = F
)
```

#### Dummy autocoups

```{r}
#| label: tbl-demomodel2
#| tbl-cap: "The Impact of Autocoups on Democratization: Dummy autocoups"
#| results: asis


demo_model1 <- plm(
  Attempted ~ Autocoup + Coup + GDP_pc + GDP_trend + pop_log + violence + regime + factor(cold_war),
  index = c("ccode", "year"),
  model = "within", # fixed effect
  effect = "individual",
  data = coup_autocoup |>
    rename(Attempted = diff2, Autocoup = autocoup_attemp, Coup = coup_attemp) |>
    filter(regime != "other")
)

demo_model2 <- plm(
  Attempted ~ Autocoup + Coup + GDP_pc + GDP_trend + pop_log + violence + regime + factor(cold_war),
  index = c("ccode", "year"),
  model = "within", # fixed effect
  effect = "individual",
  data = coup_autocoup |>
    rename(Attempted = diff3, Autocoup = autocoup_attemp, Coup = coup_attemp) |>
    filter(regime != "other")
)

demo_model3 <- plm(
  Succeeded ~ Autocoup + Coup + GDP_pc + GDP_trend + pop_log + violence + regime + factor(cold_war),
  index = c("ccode", "year"),
  model = "within", # fixed effect
  effect = "individual",
  data = coup_autocoup |>
    rename(Succeeded = diff2, Autocoup = autocoup_succeed, Coup = coup_succeed) |>
    filter(regime != "other")
)
demo_model4 <- plm(
  Succeeded ~ Autocoup + Coup + GDP_pc + GDP_trend + pop_log + violence + regime + factor(cold_war),
  index = c("ccode", "year"),
  model = "within", # fixed effect
  effect = "individual",
  data = coup_autocoup |>
    rename(Succeeded = diff3, Autocoup = autocoup_succeed, Coup = coup_succeed) |>
    filter(regime != "other")
)


stargazer(demo_model1, demo_model2, demo_model3, demo_model4,
  type = "text",
  float = F,
  header = F,
  dep.var.caption = "Dependent variable: Differences of Polity scores",
  covariate.labels = c(
    "Autocoup", "Coup", "GDP per Capita",
    "Economic Trend", "Log Population", "Political Violence",
    "Regime: Dominant-party", "\\hspace{1.5cm} Military", "\\hspace{1.5cm} Monarchy", "\\hspace{1.5cm} Personal", "Cold War"
  ),
  summary.logical = F,
  column.sep.width = "20pt",
  # font.size = "footnotesize",
  df = F
)
```

```{r}
coup_autocoup |>
  filter(regime %in% c("democracy", "dominant-party", "military", "personal")) |>
  group_by(year, regime) |> # 按年份和政体类型分组
  summarise(mean_polity5 = mean(polity5, na.rm = TRUE)) |>
  ungroup() |>
  ggplot(aes(x = year, y = mean_polity5, color = regime)) +
  geom_line(size = 1) + # 画趋势线
  geom_point(size = 2) + # 标出数据点
  labs(
    title = "不同政体类型的 polity5 年均指数",
    x = "年份",
    y = "平均 polity5 指数",
    color = "政体类型"
  ) + # 图例
  theme_minimal()
```

```{r}
#| label: backup_code
# targets <- tibble(
#   leader = c(
#     "Avril",
#     "Cabral",
#     "Bouterse",
#     "Castello Branco",
#     "Padilla Aranciba",
#     "Aramburu",
#     "Mendez Manfredini",
#     "Dioncounda Traore",
#     "Soglo",
#     "Ahomadegbe",
#     "Ironsi",
#     "Ironsi",
#     "Gowon",
#     "Micombero",
#     "Salem Aref",
#     "Ziaur Rahman",
#     "Boun Oum",
#     "Van Thieu"
#   ),
#   coup_date = ymd(c(
#     "1988-06-20",
#     "1963-09-25",
#     "1980-02-25",
#     "1964-03-30",
#     "1978-07-21",
#     "1955-09-16",
#     "1976-06-12",
#     "2012-03-22",
#     "1965-11-29",
#     "1972-10-26",
#     "1966-01-15",
#     "1966-07-29",
#     "1966-01-15",
#     "1966-07-08",
#     "1963-11-18",
#     "1975-08-15",
#     "1960-08-09",
#     "1965-01-27"
#   ))
# )
```

## Upload Datasets

```{bash}
#| label: upload

git add .
git commit -m "Version $(date +%Y-%m-%d)"
git push
```
